---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Genvoyabub <-read.csv(file="Genvoyabub.csv",header=TRUE)
abacavirinol<-read.csv(file="abacavirinol.csv",header=TRUE)
Atriplavast<-read.csv(file="Atriplavast.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?


# Genvoyabub

We will subset the data by sex to see if the drug is sex specific.
```{r}
tabsexinfected <- xtabs(~infected+group,data=Genvoyabub)
tabsexinfected
barchartGC(tabsexinfected,type = "percent")
```

In the barchart we see that there is a slight difference in those that took the placebo and got aids to those that took the drug, but there is not a big enough difference to be alarmed that either causes one to catch aids. We will conduct further test to analyze the placebo and drug.


```{r}
colPerc(tabsexinfected)
```

```{r}
rowPerc(tabsexinfected)
```

```{r}
mygenvo <-chisqtestGC(tabsexinfected, graph = TRUE) 
mygenvo
```


```{r}
myfisher <- fisher.test(tabsexinfected)
myfisher
```



```{r}
GenvoyabubM <- filter(Genvoyabub,sex=="M")
```

```{r}
myfisher <- fisher.test(tabsexinfected)
myfisher
```

```{r}
tabmales <- xtabs(~infected+group,data=GenvoyabubM)
tabmales
barchartGC(tabmales,type = "percent")
```

```{r}
colPerc(tabmales)
```

```{r}
rowPerc(tabmales)
```

```{r}
mygenvo1 <-chisqtestGC(tabmales, graph = TRUE) 
mygenvo1
```

```{r}
myfisher1 <- fisher.test(tabmales)
myfisher1
```

```{r}
GenvoyabubF <- filter(Genvoyabub,sex=="F")
```

```{r}
tabfemales <- xtabs(~infected+group,data=GenvoyabubF)
tabfemales
barchartGC(tabfemales,type = "percent")
```

```{r}
colPerc(tabfemales)
```

```{r}
rowPerc(tabfemales)
```

```{r}
mygenvo2 <-chisqtestGC(tabfemales, graph = TRUE) 
mygenvo2
```

```{r}
myfisher2 <- fisher.test(tabfemales)
myfisher2
```

# Atriplavast

We will subset the data by sex to see if the drug is sex specific.



# abacavirinol

We will subset the data by sex to see if the drug is sex specific.






